\section{Vulnerability Identification}
\label{detection}

The task of identifying inputs that trigger sanitizers is carried out mostly using dynamic analysis techniques.
This is largely dictated by the structure of the competition, since the targets are provided in OSS-Fuzz format with specific harnesses to access the application functionality.

At a high level, there are a number of fuzzers that operate in different ways: The \afluzzer agent uses a custom version of the AFL++ tool~\cite{aflplusplus} to fuzz a C/C++ application; The \jazzmine agent uses a custom version of the Jazzer tool~\cite{jazzer} to fuzz a Java application.

In addition, there is a grammar-focused agent, called \grammarguy, whose task is to develop grammars that can be used to generate input seeds that conform to specific formats.

Finally, there is an agent, called \quickseed, who uses LLM-based reasoning to produce interesting inputs for a harness.

Every agent that can produce interesting seeds (i.e., both the fuzzers and the input generators) contributes their findings to a seed repository called \seedsync, which takes care of distributing the seed across all the fuzzing agents.

However, not all vulnerability finding is performed using fuzzing.
There is an agent, called \lluminar, that looks at every function using a custom LLM, and determines if the function is vulnerable.
If that's the case, then the LLM reasons about how to provide an input that can reach the vulnerable function using LLM-based reasoning. 

%ijon system will be included 

\input{sections/coverage_guided_fuzzing}
\input{sections/afluzzer}
\input{sections/jazzmine}
\input{sections/grammar-fuzzing}
\input{sections/discoveryguy}
\input{sections/lluminar}
\input{sections/quickseed}
\input{sections/aijon}

\input{sections/povguy}

If the crash is not a duplicate it goes to the submitter agent which submitted to the scoring system'

