% ============================================================
%  ARTIPHISHELL REFERENCES
%  Bibliography entries for the Artiphishell paper
%  (DEF CON 2025 / DARPA AIxCC)
%
%  Entries that already exist in frontmatter/references.tex
%  with different keys are aliased here under the paper's
%  original citation keys.
% ============================================================

% ---- Alias entries (paper key differs from existing key) ----

\bibitem{aixcc}
DARPA, ``AIxCC: AI Cyber Challenge,'' 2025, \url{https://aicyberchallenge.com/}.

\bibitem{semgrep}
G. Bennett, T. Hall, E. Winter, and S. Mayfield, ``Semgrep$^+$: Improving the limited performance of static application security testing (SAST) tools,'' in \textit{Int. Conf. on Evaluation and Assessment in Software Engineering (EASE)}, 2024.

\bibitem{aschermann2020ijon}
C. Aschermann, S. Schumilo, A. Abbasi, and T. Holz, ``IJON: Exploring deep state spaces via fuzzing,'' in \textit{2020 IEEE Symposium on Security and Privacy (SP)}, 2020, pp. 1597--1612.

% ---- New entries (not in frontmatter/references.tex) ----

\bibitem{sarif}
OASIS, ``Static Analysis Results Interchange Format (SARIF) Version 2.1.0,'' 2023, \url{https://docs.oasis-open.org/sarif/sarif/v2.1.0/sarif-v2.1.0.html}.

\bibitem{oss-fuzz}
Google, ``OSS-Fuzz,'' 2016, \url{https://google.github.io/oss-fuzz/}.

\bibitem{libfuzzer}
LLVM, ``libFuzzer -- a library for coverage-guided fuzz testing,'' 2025, \url{https://llvm.org/docs/LibFuzzer.html}.

\bibitem{honggfuzz}
R. Swiecki, ``Honggfuzz: Security Oriented Fuzzer with Feedback-Driven Mutations,'' 2019, \url{https://github.com/google/honggfuzz}.

\bibitem{aflplusplus}
A. Fioraldi, D. Maier, H. Eissfeldt, and M. Heuse, ``AFL++: Combining incremental steps of fuzzing research,'' in \textit{Proceedings of the USENIX Conference on Offensive Technologies (WOOT)}, 2020.

\bibitem{jazzer}
Code Intelligence, ``Jazzer: Coverage-Guided, In-Process Fuzzer for the JVM,'' 2025, \url{https://github.com/CodeIntelligenceTesting/jazzer}.

\bibitem{aixcc:toast}
DARPA, ``The Open Application Security Testing (TOAST),'' 2025, \url{https://github.com/aixcc-finals/toast}.

\bibitem{afl}
M. Zalewski, ``American Fuzzy Lop (AFL),'' 2015, \url{https://lcamtuf.coredump.cx/afl/}.

\bibitem{bohme2016aflfast}
M. Böhme, V. Pham, and A. Roychoudhury, ``Coverage-based greybox fuzzing as Markov chain,'' in \textit{Proceedings of the ACM SIGSAC Conference on Computer and Communications Security (CCS)}, 2016.

\bibitem{lyu2019mopt}
C. Lyu, S. Ji, C. Zhang, Y. Li, W. Lee, Y. Song, and R. Beyah, ``MOPT: Optimized mutation scheduling for fuzzers,'' in \textit{Proceedings of the USENIX Security Symposium}, 2019.

\bibitem{aschermann2019redqueen}
C. Aschermann, S. Schumilo, T. Blazytko, R. Gawlik, and T. Holz, ``REDQUEEN: Fuzzing with input-to-state correspondence,'' in \textit{Proceedings of the Network and Distributed System Security Symposium (NDSS)}, 2019.

\bibitem{meng2021:Bran}
D. Meng, M. Guerriero, A. Machiry, H. Aghakhani, P. Bose, A. Continella, C. Kruegel, and G. Vigna, ``Bran: Reduce vulnerability search space in large open-source repositories by learning bug symptoms,'' in \textit{Proceedings of the ACM Asia Conference on Computer and Communications Security (AsiaCCS)}, Hong Kong, China, June 2021.

\bibitem{Moshtari2013}
S. Moshtari, A. Sami, and M. Azimi, ``Using complexity metrics to improve software security,'' \textit{Computer Fraud \& Security}, vol. 2013, no. 5, pp. 8--17, Elsevier, 2013.

\bibitem{Neuhaus2007}
S. Neuhaus, T. Zimmermann, C. Holler, and A. Zeller, ``Predicting vulnerable software components,'' in \textit{Proceedings of the ACM Conference on Computer and Communications Security (CCS)}, 2007.

\bibitem{codeql}
Code Intelligence, ``CodeQL,'' 2025, \url{https://codeql.github.com/}.

\bibitem{nautilus}
C. Aschermann, T. Frassetto, T. Holz, P. Jauernig, A. Sadeghi, and D. Teuchert, ``NAUTILUS: Fishing for deep bugs with grammars,'' in \textit{Proceedings of the Network and Distributed System Security Symposium (NDSS)}, 2019.

\bibitem{benzene}
Y. Park, H. Lee, J. Jung, H. Koo, and H. K. Kim, ``BENZENE: A practical root cause analysis system with an under-constrained state mutation,'' in \textit{Proceedings of the IEEE Symposium on Security and Privacy (SP)}, 2024.

\bibitem{aurora}
T. Blazytko, M. Schlögel, C. Aschermann, A. Abbasi, J. Frank, S. Wörner, and T. Holz, ``AURORA: Statistical crash analysis for automated root cause explanation,'' in \textit{Proceedings of the USENIX Security Symposium}, 2020.

\bibitem{mei2024arvo}
X. Mei, P. S. Singaria, J. Del Castillo, H. Xi, T. Bao, R. Wang, Y. Shoshitaishvili, A. Doup\'{e}, H. Pearce, B. Dolan-Gavitt, and others, ``Arvo: Atlas of reproducible vulnerabilities for open source software,'' \textit{arXiv preprint arXiv:2408.02153}, 2024.

\bibitem{yang2024qwen2}
A. Yang, B. Yang, B. Hui, B. Zheng, B. Yu, C. Zhou, C. Li, C. Chengyuan, D. Liu, F. Huang, and others, ``Qwen2 technical report,'' \textit{arXiv preprint arXiv:2407.10671}, 2024.

\bibitem{grammarinator}
R. Hodován, Á. Kiss, and T. Gyimóthy, ``Grammarinator: A grammar-based open source fuzzer,'' in \textit{Proceedings of the 9th ACM SIGSOFT International Workshop on Automating Test Case Design, Selection, and Evaluation (A-TEST 2018)}, Lake Buena Vista, FL, USA, pp. 45--48, 2018.

% ---- Artiphishell Related Work References ----

\bibitem{legoues2012genprog}
C. Le Goues, T. Nguyen, S. Forrest, and W. Weimer, ``GenProg: A generic method for automatic software repair,'' \textit{IEEE Transactions on Software Engineering}, vol. 38, no. 1, pp. 54--72, 2012.

\bibitem{nguyen2013semfix}
H. D. T. Nguyen, D. Qi, A. Roychoudhury, and S. Chandra, ``SemFix: Program repair via semantic analysis,'' in \textit{2013 35th International Conference on Software Engineering (ICSE)}, IEEE, 2013, pp. 772--781.

\bibitem{mechtaev2016angelix}
S. Mechtaev, J. Yi, and A. Roychoudhury, ``Angelix: Scalable multiline program patch synthesis via symbolic analysis,'' in \textit{Proceedings of the 38th International Conference on Software Engineering (ICSE)}, ACM, 2016, pp. 691--701.

\bibitem{pearce2023zeroshotvulnrepair}
H. Pearce, B. Tan, B. Ahmad, R. Karri, and B. Dolan-Gavitt, ``Examining zero-shot vulnerability repair with large language models,'' in \textit{2023 IEEE Symposium on Security and Privacy (SP)}, IEEE, 2023, pp. 2339--2356.

\bibitem{xia2024fuzz4all}
C. S. Xia, M. Paltenghi, J. L. Tian, M. Pradel, and L. Zhang, ``Fuzz4All: Universal fuzzing with large language models,'' in \textit{Proceedings of the IEEE/ACM 46th International Conference on Software Engineering (ICSE)}, ACM, 2024.

\bibitem{yu2025patchagent}
Z. Yu, Z. Guo, Y. Wu, J. Yu, M. Xu, D. Mu, Y. Chen, and X. Xing, ``PATCHAGENT: A practical program repair agent mimicking human expertise,'' in \textit{34th USENIX Security Symposium (USENIX Security 25)}, 2025, pp. 4381--4400.

\bibitem{deng2023titanfuzz}
Y. Deng, C. S. Xia, H. Peng, C. Yang, and L. Zhang, ``Large language models are zero-shot fuzzers: Fuzzing deep-learning libraries via large language models,'' in \textit{Proceedings of the 32nd ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA)}, ACM, 2023.

\bibitem{meng2024chatafl}
R. Meng, M. Mirchev, M. B\"{o}hme, and A. Roychoudhury, ``Large language model guided protocol fuzzing,'' in \textit{Proceedings of the Network and Distributed System Security Symposium (NDSS)}, 2024.

\bibitem{zhang2026sokaixcc}
C. Zhang, Y. Park, F. Fleischer, Y.-F. Fu, J. Kim, D. Kim, Y. Kim, Q. Xu, A. Chin, Z. Sheng, H. Zhao, B. J. Lee, J. Wang, M. Pelican, D. J. Musliner, J. Huang, J. Silliman, M. Mcdaniel, J. Casavant, I. Goldthwaite, N. Vidovich, M. Lehman, and T. Kim, ``SoK: DARPA's AI Cyber Challenge (AIxCC): Competition design, architectures, and lessons learned,'' \textit{arXiv preprint arXiv:2602.07666}, 2026.
