% ============================================================
%  MANGO REFERENCES
%  Bibliography entries for the Operation Mango paper
%  (USENIX Security 2024)
%
%  Entries that already exist in frontmatter/references.tex
%  with different keys are duplicated here under the paper's
%  original citation keys.
% ============================================================

% ---- Duplicate entries (paper key differs from existing key) ----

\bibitem{karonte}
N. Redini, A. Machiry, R. Wang, C. Spensky, A. Continella, Y. Shoshitaishvili, C. Kruegel, and G. Vigna, ``Karonte: Detecting insecure multi-binary interactions in embedded firmware,'' in \textit{2020 IEEE Symposium on Security and Privacy (SP)}, IEEE, 2020, pp. 1544--1561.

\bibitem{SaTC}
L. Chen, Y. Wang, Q. Cai, Y. Zhan, H. Hu, J. Linghu, Q. Hou, C. Zhang, H. Duan, and Z. Xue, ``Sharing more and checking less: Leveraging common input keywords to detect bugs in embedded systems,'' in \textit{USENIX Security Symposium}, 2021, pp. 303--319.

\bibitem{chen2016towards}
D. D. Chen, M. Woo, D. Brumley, and M. Egele, ``Towards automated dynamic analysis for Linux-based embedded firmware,'' in \textit{NDSS}, vol. 1, 2016.

\bibitem{zheng2019firm}
Y. Zheng, A. Davanian, H. Yin, C. Song, H. Zhu, and L. Sun, ``FIRM-AFL: High-throughput greybox fuzzing of IoT firmware via augmented process emulation,'' in \textit{USENIX Security Symposium}, 2019, pp. 1099--1114.

\bibitem{greenhouse}
H. J. Tay, K. Zeng, J. M. Vadayath, A. Raj, A. Dutcher, T. Reddy, W. Gibbs, Z. L. Basque, F. Dong, A. Doupe, T. Bao, Y. Shoshitaishvili, and R. Wang, ``Greenhouse: Single-service rehosting of Linux-based firmware binaries in user-space emulation,'' in \textit{USENIX Security Symposium 2023}, 2023.

% ---- New entries (not in frontmatter/references.tex) ----

\bibitem{kudelski}
{Kudelski IoT}, ``Why is it so hard to keep IoT devices up to date and secure?'' 2023, \url{https://www.kudelski-iot.com/insights/why-is-it-so-hard-to-keep-iot-devices-up-to-date-and-secure}.

\bibitem{cybertalk}
{CyberTalk}, ``FBI issues warning, unpatched and outdated IoT,'' 2023, \url{https://www.cybertalk.org/fbi-issues-warning-unpatched-outdated-iot/}.

\bibitem{matter}
{Connectivity Standards Alliance}, ``Build with Matter | Smart home device solution -- CSA-IOT,'' \url{https://csa-iot.org/all-solutions/matter/}.

\bibitem{zigbee}
{Connectivity Standards Alliance}, ``Zigbee | Complete IOT solution -- CSA-IOT,'' \url{https://csa-iot.org/all-solutions/zigbee/}.

\bibitem{gbhackers}
Balaji, ``A zero-day vulnerability in TP-link router let hackers gain admin privilege and take full control of it remotely,'' 2019, \url{https://gbhackers.com/tp-link-router/}.

\bibitem{scmagazine}
{SC Staff}, ``Netcomm, TP-Link routers impacted by critical bugs,'' 2023, \url{https://www.scmagazine.com/brief/device-security/netcomm-tp-link-routers-impacted-by-critical-bugs}.

\bibitem{zheng2022efficient}
Y. Zheng, Y. Li, C. Zhang, H. Zhu, Y. Liu, and L. Sun, ``Efficient greybox fuzzing of applications in Linux-based IoT devices via enhanced user-mode emulation,'' in \textit{Proc. 31st ACM SIGSOFT Int. Symposium on Software Testing and Analysis}, 2022, pp. 417--428.

\bibitem{qasem2021automatic}
A. Qasem, P. Shirani, M. Debbabi, L. Wang, and B. L. Agba, ``Automatic vulnerability detection in embedded devices and firmware: Survey and layered taxonomies,'' \textit{ACM Computing Surveys}, vol. 54, no. 2, pp. 1--42, 2021.

\bibitem{costin2014large}
A. Costin, J. Zaddach, A. Francillon, and D. Balzarotti, ``A large-scale analysis of the security of embedded firmwares,'' in \textit{23rd USENIX Security Symposium}, 2014, pp. 95--110.

\bibitem{celik2018sensitive}
Z. B. Celik, L. Babun, A. K. Sikder, H. Aksu, G. Tan, P. McDaniel, and A. S. Uluagac, ``Sensitive information tracking in commodity IoT,'' in \textit{27th USENIX Security Symposium}, 2018, pp. 1687--1704.

\bibitem{mandal2020cross}
A. Mandal, P. Ferrara, Y. Khlyebnikov, A. Cortesi, and F. Spoto, ``Cross-program taint analysis for IoT systems,'' in \textit{Proc. 35th Annual ACM Symposium on Applied Computing}, 2020, pp. 1944--1952.

\bibitem{qemu}
{QEMU}, ``QEMU,'' \url{https://www.qemu.org}.

\bibitem{binwalk}
{ReFirmLabs}, ``Binwalk: Firmware analysis tool,'' \url{https://github.com/ReFirmLabs/binwalk}.

\bibitem{clause2007dytan}
J. Clause, W. Li, and A. Orso, ``Dytan: A generic dynamic taint analysis framework,'' in \textit{Proc. 2007 Int. Symposium on Software Testing and Analysis}, 2007, pp. 196--206.

\bibitem{saxena2008efficient}
P. Saxena, R. Sekar, and V. Puranik, ``Efficient fine-grained binary instrumentation with applications to taint-tracking,'' in \textit{Proc. 6th Annual IEEE/ACM Int. Symposium on Code Generation and Optimization}, 2008, pp. 74--83.

\bibitem{balakrishnan2005codesurfer}
G. Balakrishnan, R. Gruian, T. Reps, and T. Teitelbaum, ``CodeSurfer/x86: A platform for analyzing x86 executables,'' in \textit{Int. Conf. on Compiler Construction}, Springer, 2005, pp. 250--254.

\bibitem{balakrishnan2004analyzing}
G. Balakrishnan and T. Reps, ``Analyzing memory accesses in x86 executables,'' in \textit{Int. Conf. on Compiler Construction}, Springer, 2004, pp. 5--23.

\bibitem{zhang2007parameter}
J. Zhang, R. Zhao, and J. Pang, ``Parameter and return-value analysis of binary executables,'' in \textit{31st Annual Int. Computer Software and Applications Conf. (COMPSAC 2007)}, IEEE, 2007, pp. 501--508.

\bibitem{wang2017angr}
F. Wang and Y. Shoshitaishvili, ``Angr: The next generation of binary analysis,'' in \textit{2017 IEEE Cybersecurity Development (SecDev)}, IEEE, 2017, pp. 8--9.

\bibitem{kudrjavets2022unexplored}
G. Kudrjavets, A. Kumar, N. Nagappan, and A. Rastogi, ``The unexplored terrain of compiler warnings,'' in \textit{Proc. 44th Int. Conf. on Software Engineering: Software Engineering in Practice}, 2022, pp. 283--284.

\bibitem{votipka2019observational}
D. Votipka, S. Rabin, K. Micinski, J. S. Foster, and M. L. Mazurek, ``An observational investigation of reverse engineers' process and mental models,'' in \textit{Extended Abstracts of the 2019 CHI Conf. on Human Factors in Computing Systems}, 2019, pp. 1--6.
