Skilled security analysts find vulnerabilities through practitioner knowledge: they know which data flows look exploitable, which code patterns signal real bugs versus false alarms, and which analysis techniques to combine when one alone falls short. Automated tools can detect potential vulnerabilities at scale, but they discard this practitioner reasoning in the process. The result is thousands of candidates that a human must still triage. This dissertation encodes three forms of practitioner knowledge into automated systems, making vulnerability discovery both scalable and autonomous.

First, Operation Mango (USENIX Security 2024) encodes value-level reasoning. When a human analyst traces a data flow from source to sink, they track how values are transformed along the way: was the input truncated by \texttt{snprintf()}? Converted to an integer by \texttt{itoa()}? MangoDFA, a novel static data-flow analysis for firmware binaries, captures this reasoning through Rich Expressions, which record transformation history rather than binary taint bits. On the standard Karonte dataset, Mango analyzed all 3,599 binaries (a 27$\times$ increase in scope over prior work) while averaging 8 minutes per binary. On a large-scale corpus of 1,698 firmware images containing 770,374 binaries, Mango produced 10,834 ranked vulnerability alerts and confirmed 166 exploitable vulnerabilities.

Second, Artiphishell (DEF CON 2025) encodes multi-technique workflow knowledge. Experienced security teams do not rely on a single tool; they cross-reference fuzzer crashes against static analysis findings, use debuggers to localize root causes, and validate patches against regression suites. Artiphishell, a fully autonomous Cyber Reasoning System built for the DARPA AI Cyber Challenge, encodes this workflow into a multi-agent architecture where coverage-guided fuzzing, grammar-based fuzzing, LLM-powered scanning, root-cause analysis, and AI-driven patching coordinate through a shared Analysis Graph. Artiphishell advanced to the AIxCC semi-finals.

Third, we propose encoding path feasibility reasoning through symbolic execution on angr's AIL intermediate language. Practitioners mentally simulate program execution to determine whether a flagged path is actually reachable. AIL carries recovered type information and structured control flow, enabling tighter constraints and fewer infeasible paths. This engine plugs directly into MangoDFA, performing targeted symbolic exploration of static candidates to determine path feasibility and generate concrete triggering inputs.
