% ====================
% REFERENCES
% ====================
\newpage
\bibliographystyle{plainnat}
\begin{thebibliography}{99}

\bibitem{redini2020karonte}
N. Redini, A. Machiry, R. Wang, C. Spensky, A. Continella, Y. Shoshitaishvili, C. Kruegel, and G. Vigna, ``Karonte: Detecting insecure multi-binary interactions in embedded firmware,'' in \textit{2020 IEEE Symposium on Security and Privacy (SP)}, IEEE, 2020, pp. 1544--1561.

\bibitem{chen2021satc}
L. Chen, Y. Wang, Q. Cai, Y. Zhan, H. Hu, J. Linghu, Q. Hou, C. Zhang, H. Duan, and Z. Xue, ``Sharing more and checking less: Leveraging common input keywords to detect bugs in embedded systems,'' in \textit{USENIX Security Symposium}, 2021, pp. 303--319.

\bibitem{cheng2018dtaint}
K. Cheng, Q. Li, L. Wang, Q. Chen, Y. Zheng, L. Sun, and Z. Liang, ``DTaint: Detecting the taint-style vulnerability in embedded device firmware,'' in \textit{48th Annual IEEE/IFIP Int. Conf. on Dependable Systems and Networks (DSN)}, IEEE, 2018, pp. 430--441.

\bibitem{gotovchits2018saluki}
I. Gotovchits, R. Van Tonder, and D. Brumley, ``Saluki: Finding taint-style vulnerabilities with static property checking,'' in \textit{NDSS Workshop on Binary Analysis Research}, 2018.

\bibitem{vadayath2022arbiter}
J. Vadayath, M. Eckert, K. Zeng, N. Weideman, G. P. Menon, Y. Fratantonio, D. Balzarotti, A. Doup\'{e}, T. Bao, R. Wang et al., ``Arbiter: Bridging the static and dynamic divide in vulnerability discovery on binary programs,'' in \textit{31st USENIX Security Symposium}, 2022, pp. 413--430.

\bibitem{luo2022tchecker}
C. Luo, P. Li, and W. Meng, ``Tchecker: Precise static inter-procedural analysis for detecting taint-style vulnerabilities in PHP applications,'' in \textit{2022 ACM SIGSAC Conf. on Computer and Communications Security}, 2022, pp. 2175--2188.

\bibitem{bennett2024semgrep}
G. Bennett, T. Hall, E. Winter, and S. Mayfield, ``Semgrep$^+$: Improving the limited performance of static application security testing (SAST) tools,'' in \textit{Int. Conf. on Evaluation and Assessment in Software Engineering (EASE)}, 2024.

\bibitem{chen2016firmadyne}
D. D. Chen, M. Woo, D. Brumley, and M. Egele, ``Towards automated dynamic analysis for Linux-based embedded firmware,'' in \textit{NDSS}, vol. 1, 2016.

\bibitem{kim2020firmae}
M. Kim, D. Kim, E. Kim, S. Kim, Y. Jang, and Y. Kim, ``FirmAE: Towards large-scale emulation of IoT firmware for dynamic analysis,'' in \textit{Annual Computer Security Applications Conf.}, 2020, pp. 733--745.

\bibitem{zaddach2014avatar}
J. Zaddach, L. Bruno, A. Francillon, D. Balzarotti et al., ``AVATAR: A framework to support dynamic security analysis of embedded systems' firmwares,'' in \textit{NDSS Symposium}, vol. 14, 2014, pp. 1--16.

\bibitem{muench2018avatar2}
M. Muench, D. Nisi, A. Francillon, and D. Balzarotti, ``Avatar 2: A multi-target orchestration platform,'' in \textit{Proc. Workshop Binary Anal. Res. (Colocated NDSS Symp.)}, vol. 18, 2018, pp. 1--11.

\bibitem{tay2023greenhouse}
H. J. Tay, K. Zeng, J. M. Vadayath, A. Raj, A. Dutcher, T. Reddy, W. Gibbs, Z. L. Basque, F. Dong, A. Doupe, T. Bao, Y. Shoshitaishvili, and R. Wang, ``Greenhouse: Single-service rehosting of Linux-based firmware binaries in user-space emulation,'' in \textit{USENIX Security Symposium 2023}, 2023.

\bibitem{kammerstetter2014prospect}
M. Kammerstetter, C. Platzer, and W. Kastner, ``Prospect: Peripheral proxying supported embedded code testing,'' in \textit{ACM Asia Conf. on Computer and Communications Security (ASIACCS)}, 2014.

\bibitem{talebi2018charm}
S. M. S. Talebi, H. Tavakoli, H. Zhang, Z. Zhang, A. A. Sani, and Z. Qian, ``Charm: Facilitating dynamic analysis of device drivers of mobile systems,'' in \textit{USENIX Security Symposium (USENIX)}, 2018.

\bibitem{koscher2015surrogates}
K. Koscher, T. Kohno, and D. Molnar, ``SURROGATES: Enabling near-real-time dynamic analyses of embedded systems,'' in \textit{USENIX Workshop on Offensive Technologies (WOOT)}, 2015.

\bibitem{clements2020halucinator}
A. A. Clements, E. Gustafson, T. Scharnowski, P. Grosen, D. Fritz, C. Kruegel, G. Vigna, S. Bagchi, and M. Payer, ``HALucinator: Firmware re-hosting through abstraction layer emulation,'' in \textit{29th USENIX Security Symposium}, 2020, pp. 1201--1218.

\bibitem{mera2021dice}
A. Mera, B. Feng, L. Lu, and E. Kirda, ``DICE: Automatic emulation of DMA input channels for dynamic firmware analysis,'' in \textit{IEEE Symposium on Security and Privacy (SP)}, 2021.

\bibitem{zheng2019firmafl}
Y. Zheng, A. Davanian, H. Yin, C. Song, H. Zhu, and L. Sun, ``FIRM-AFL: High-throughput greybox fuzzing of IoT firmware via augmented process emulation,'' in \textit{USENIX Security Symposium}, 2019, pp. 1099--1114.

\bibitem{feng2021snipuzz}
X. Feng, R. Sun, X. Zhu, M. Xue, S. Wen, D. Liu, S. Nepal, and Y. Xiang, ``Snipuzz: Black-box fuzzing of IoT firmware via message snippet inference,'' in \textit{2021 ACM SIGSAC Conf. on Computer and Communications Security}, 2021, pp. 337--350.

\bibitem{srivastava2019firmfuzz}
P. Srivastava, H. Peng, J. Li, H. Okhravi, H. Shrobe, and M. Payer, ``FirmFuzz: Automated IoT firmware introspection and analysis,'' in \textit{2nd Int. ACM Workshop on Security and Privacy of the Internet-of-Things}, 2019, pp. 15--21.

\bibitem{king1976symbolic}
J. C. King, ``Symbolic execution and program testing,'' \textit{Communications of the ACM}, vol. 19, no. 7, pp. 385--394, 1976.

\bibitem{shoshitaishvili2016sok}
Y. Shoshitaishvili, R. Wang, C. Salls, N. Stephens, M. Polino, A. Dutcher, J. Grosen, S. Feng, C. Hauser, C. Kruegel et al., ``Sok: (State of) the art of war: Offensive techniques in binary analysis,'' in \textit{2016 IEEE Symposium on Security and Privacy (SP)}, 2016, pp. 138--157.

\bibitem{davidson2013fie}
D. Davidson, B. Moench, T. Ristenpart, and S. Jha, ``FIE on firmware: Finding vulnerabilities in embedded systems using symbolic execution,'' in \textit{USENIX Security Symposium}, 2013, pp. 463--478.

\bibitem{shoshitaishvili2015firmalice}
Y. Shoshitaishvili, R. Wang, C. Hauser, C. Kruegel, and G. Vigna, ``Firmalice: Automatic detection of authentication bypass vulnerabilities in binary firmware,'' in \textit{NDSS}, vol. 1, 2015, pp. 1--1.

\bibitem{ming2016straighttaint}
J. Ming, D. Wu, J. Wang, G. Xiao, and P. Liu, ``StraightTaint: Decoupled offline symbolic taint analysis,'' in \textit{31st IEEE/ACM Int. Conf. on Automated Software Engineering}, 2016, pp. 308--319.

\bibitem{ming2015taintpipe}
J. Ming, D. Wu, G. Xiao, J. Wang, and P. Liu, ``TaintPipe: Pipelined symbolic taint analysis,'' in \textit{24th USENIX Security Symposium}, 2015, pp. 65--80.

\bibitem{krishnamoorthy2010tackling}
S. Krishnamoorthy, M. S. Hsiao, and L. Lingappan, ``Tackling the path explosion problem in symbolic execution-driven test generation for programs,'' in \textit{2010 19th IEEE Asian Test Symposium}, IEEE, 2010, pp. 59--64.

\bibitem{darpa2025aixcc}
DARPA, ``AIxCC: AI Cyber Challenge,'' 2025, \url{https://aicyberchallenge.com/}.

\bibitem{statista2024iot}
Statista, ``Number of Internet of Things (IoT) connected devices worldwide from 2019 to 2030,'' 2024, \url{https://www.statista.com/statistics/1183457/iot-connected-devices-worldwide/}.

\bibitem{antonakakis2017mirai}
M. Antonakakis, T. April, M. Bailey, M. Bernhard, E. Bursztein, J. Cochran, Z. Durumeric, J. A. Halderman, L. Invernizzi, M. Kallitsis et al., ``Understanding the Mirai botnet,'' in \textit{26th USENIX Security Symposium}, 2017, pp. 1093--1110.

\bibitem{darpa2016cgc}
DARPA, ``Cyber Grand Challenge,'' 2016, \url{https://www.darpa.mil/program/cyber-grand-challenge}.

\bibitem{gibbs2024mango}
W. Gibbs, A. S. Raj, J. M. Vadayath, H. J. Tay, J. Miller, A. Ajayan, Z. L. Basque, A. Dutcher, F. Dong, X. Maso, C. Vigna, C. Kruegel, A. Doup\'{e}, Y. Shoshitaishvili, and R. Wang, ``Operation Mango: Scalable discovery of taint-style vulnerabilities in binary firmware services,'' in \textit{33rd USENIX Security Symposium}, 2024.

\bibitem{thapa2022vuldeepecker}
C. Thapa, S. I. Jang, M. E. Ahmed, S. Camtepe, J. Pieprzyk, and S. Nepal, ``Transformer-based language models for software vulnerability detection,'' in \textit{Proceedings of the 38th Annual Computer Security Applications Conference}, 2022, pp. 481--496.

\bibitem{wheeler2001sloc}
D. A. Wheeler, ``More than a gigabuck: Estimating GNU/Linux's size,'' 2001, \url{https://dwheeler.com/sloc/redhat71-v1/redhat71sloc.html}.

\bibitem{iotanalytics2025}
IoT Analytics, ``State of IoT -- Spring 2025: Number of connected IoT devices growing 14\% to 21.1 billion,'' 2025, \url{https://iot-analytics.com/number-connected-iot-devices/}.

\bibitem{cisco2020air}
Cisco, ``Cisco Annual Internet Report (2018--2023) White Paper,'' 2020, \url{https://www.cisco.com/c/en/us/solutions/collateral/executive-perspectives/annual-internet-report/white-paper-c11-741490.html}.

\bibitem{cybersecventures2025}
S. Morgan, ``Cybercrime to cost the world \$12.2 trillion annually by 2031,'' Cybersecurity Ventures, 2025, \url{https://cybersecurityventures.com/official-cybercrime-report-2025/}.

\bibitem{nvd2024stats}
NIST, ``National Vulnerability Database: CVE statistics,'' 2024, \url{https://nvd.nist.gov/vuln/search/statistics}. Over 40,000 CVEs published in 2024.

\bibitem{isc2workforce2024}
ISC2, ``2024 ISC2 Cybersecurity Workforce Study,'' 2024, \url{https://www.isc2.org/Insights/2024/10/ISC2-2024-Cybersecurity-Workforce-Study}.

\bibitem{johnson2013staticanalysis}
B. Johnson, Y. Song, E. Murphy-Hill, and R. Bowdidge, ``Why don't software developers use static analysis tools to find bugs?'' in \textit{2013 35th Int. Conf. on Software Engineering (ICSE)}, IEEE, 2013, pp. 672--681.

\bibitem{stephens2016driller}
N. Stephens, J. Grosen, C. Salls, A. Dutcher, R. Wang, J. Corbetta, Y. Shoshitaishvili, C. Kruegel, and G. Vigna, ``Driller: Augmenting fuzzing through selective symbolic execution,'' in \textit{Network and Distributed System Security Symposium (NDSS)}, 2016.

\bibitem{shoshitaishvili2018mechanical}
Y. Shoshitaishvili, A. Bianchi, K. Borgolte, A. Cama, J. Corbetta, F. Disperati, A. Dutcher, J. Grosen, P. Grosen, A. Machiry, C. Spensky, and G. Vigna, ``Mechanical Phish: Resilient autonomous hacking,'' \textit{IEEE Security \& Privacy}, vol. 16, no. 2, pp. 12--22, 2018.

\bibitem{cha2012mayhem}
S.~K. Cha, T. Avgerinos, A. Rebert, and D. Brumley, ``Unleashing Mayhem on binary code,'' in \textit{2012 IEEE Symposium on Security and Privacy (SP)}, IEEE, 2012, pp. 380--394.

% ---- Mango Paper References ----
\input{references/mango-refs}

% ---- Artiphishell Paper References ----
\input{references/artiphishell-refs}

\end{thebibliography}
